Fivebranes

### 2022-04-01 fivebranes/twisted.tex
merge

\begin{prop}
Let $\Obs_{fivebrane}$ be the observables of the theory on a single fivebrane on $\C^3$ after performing the holomorphic twist.
There is a quasi-isomorphism of super commutative dg algebras 
\[
\Obs_{fivebrane} (0) \simeq \Sym \left( I(0,0;1;-1)^* \right) .
\]
\end{prop}

@@

@@

>>>>

\begin{prop}
Let $\Obs_{fivebrane}$ be the observables of the theory on a single fivebrane on $\C^3$ after performing the holomorphic twist.
There is a quasi-isomorphism of super commutative dg algebras 
\[
\Obs_{fivebrane} (0) \simeq \Sym \left( I(0,0;1;-1)^* \right) .
\]
\end{prop}
\begin{proof}
This follows from Lemma \ref{lem:localops}.
In \cite{SWsuca6d} a dg lift of Kac's module $I(0,0;1;-1)$ was defined with the following bigraded pieces:
\beqn
\text{bidegree} (-1,+)\colon \quad \Hat{\Omega}_3^{2} , \qquad \text{bidegree} (0,+)\colon \quad \Hat{\Omega}^{3}_3
\eeqn
and
\beqn
\text{bidegree} (-1, -)\colon \quad \Hat{\Omega}^{3/2}_{3} \otimes R .
\eeqn
The differential is the (algebraic) de Rham differential $\del \colon \Hat{\Omega}^2 \to \Hat{\Omega}^3$. 
The differential is zero on the odd summand.
We will call this cochain complex $(E_{fivebrane}(\Hat{D}^3), \del)$.

From the description of the fields of the holomorphic twist of the single fivebrane it is easy to see that the Taylor expansion at $0 \in \C^3$ defines a cochain map
\[
(\cE_{fivebrane} (\C^3), Q) \to (E_{fivebrane}(\Hat{D}^3), \del) 
\]
That this induces a quasi-isomorphism $J_0^\infty \cE_{fivebrane} \simeq E (\Hat{D}^3)$ follows from the Dolbeault Poincar\'e lemma.
\end{proof}

@@

\parsec[s:locallieE510]

@@

\section{Example}

Consider the holomorphic local Lie algebra on $\C^n$
\[
\Omega^{0,\bu}(\C^n) 
\]
and corresponding factorization algebra $\cF = \clie^\bu(\Omega^{0,\bu}(\C^n))$. 
Now, we can restrict this to a factorization algebra on
\[
\C^n - 0 \subset \C^n
\]
that we denote by $\cF|_{\C^n - 0}$.

Next, consider the radial projection
\[
r \colon \C^n - 0 \to \R .
\]
Notice that $r_* (\cF|_{\C^n - 0})$ will not be the observables of any ordinary local Lie algebra.
Nevertheless we can come up with a nice algebraic model.

Let $A_n$ be the usual dg model for the formal punctured disk $\Hat{D}^n - 0$ as defined in \cite{FHK,GWkm}.

\begin{lem}
There is an injective map of factorization algebras on $\RR_{>0}$:
\[
\clie^\bu(\Omega^\bu(\RR_{>0}) \otimes A_n) \to r_* (\cF|_{\C^n - 0}) 
\]
which is dense in cohomology.
\end{lem}

This tells us that the correct `fields' of the dimensionally reduced theory on $\RR_{>0}$ is $\Omega^\bu(\R_{>0}) \otimes A_n$.
